---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.width = 10, fig.height = 5,
  fig.align = "center",
  fig.path  = "man/Figure/",
  dev = 'svg'
)
```
## PhenoAsync

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/kongdd/PhenoAsync.svg?branch=master)](https://travis-ci.org/kongdd/PhenoAsync)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kongdd/PhenoAsync?branch=master&svg=true)](https://ci.appveyor.com/project/kongdd/PhenoAsync)
[![codecov](https://codecov.io/gh/kongdd/PhenoAsync/branch/master/graph/badge.svg)](https://codecov.io/gh/kongdd/PhenoAsync)
<!-- badges: end -->

Extract vegetation phenology by `phenofit` (v0.2.7) at 95 flux sites.


## Vegetation Phenology Data at 95 flux sites

There are two data files: 

- `pheno_flux95_prim ((GPP_DT) v0.2.6.9000).rda`: vegetation carbon phenology from GPP_DT
- `pheno_flux95_prim ((GPP_NT) v0.2.6.9000).rda`: vegetation carbon phenology from GPP_NT

For each file, two variables are in there:

- `df_gpp_prim`: vegetation carbon phenological metrics extracted from flux sites GPP observations   
- `df_VI_prim` : vegetation greenness phenological metrics extracted from MODIS remote sensing vegetation indexes   

```{r cars}
load("INPUT/pheno_flux95_prim ((GPP_NT) v0.2.6.9000).rda")
# load("INPUT/pheno_flux95_prim ((GPP_DT) v0.2.6.9000).rda")
print(df_gpp_prim)
print(df_VI_prim)
```
<!-- # unique(df_VI_prim$sate) -->
<!-- # unique(df_VI_prim$type_VI) -->
<!-- # unique(df_VI_prim$group) -->
<!-- # unique(df_VI_prim$meth) -->

**column variables**: 

- `sate`   : MODIS satellites, one of "combined" "Aqua", and "Terra"
- `type_VI`: vegetation indexes, one of "EVI", "NDVI", "EVI_pc" and "NDVI_pc"
- `group`  : 3*3 grids id, `5` is the central grid
- `meth`   : curve fitting methods, one of 
- `flag`   : growing season id
- `origin` : first date of this year
- `others` : vegetation phenological metrics extracted by phenofit
